---
title: "Das lattice Paket"
author: "Jan-Philipp Kolb"
date: "20 Juni 2017"
output: md_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=F,warning = F)
```


## Das lattice-Paket

> It is designed to meet most typical graphics needs with minimal tuning, but can also be easily extended to handle most nonstandard requirements. 

<http://stat.ethz.ch/R-manual/R-devel/library/lattice/html/Lattice.html>

## Der Datensatz - Scores on A-level Chemistry in 1997

```{r}
library("mlmRev")
data(Chem97)
```

```{r,echo=F}
library(knitr)
cats <- c("Local Education Authority","School identifier","Student identifier","Point score on A-level Chemistry in 1997","Student's gender","Age in month, centred at 222 months or 18.5 years","Average GCSE score of individual","Average GCSE score of individual, centered at mean")
c97dat <- data.frame(variables=colnames(Chem97),categories=cats)
kable(c97dat)
```


## Histogramm mit Lattice

```{r,message=F}
library("lattice")
histogram(~ gcsescore, data = Chem97)
```

## Histogramm mit Lattice

```{r}
  histogram(~ gcsescore | factor(score),data = Chem97)
```

## Die Dichte mit Lattice zeichnen

```{r}
densityplot(~ gcsescore | factor(score), Chem97, 
	groups=gender,plot.points=FALSE,auto.key=TRUE)
```

[Einführung in das Paket lattice](http://www.isid.ac.in/~deepayan/R-tutorials/labs/04_lattice_lab.pdf)

## Boxplot mit Lattice zeichnen

```{r}
bwplot(factor(score) ~ gcsescore | gender, Chem97)
```

## Boxplot mit Lattice zeichnen

```{r}
bwplot(gcsescore ~ gender | factor(score), Chem97,
 layout = c(6, 1))
```

## Univariate Plots

```{r}
barchart(yield ~ variety | site, data = barley,
         groups = year, layout = c(1,6), stack = TRUE,
         auto.key = list(space = "right"),
         ylab = "Barley Yield (bushels/acre)",
         scales = list(x = list(rot = 45)))
```


## Densityplot

```{r}
densityplot(~height|voice.part,data=singer,layout = c(2,4),
            xlab = "Height (inches)",bw = 5)
```

## Bivariate Plots

```{r}
qq(gender ~ gcsescore | factor(score), Chem97,
   f.value = ppoints(100), type = c("p", "g"), aspect = 1)
```

## xyplot

```{r}
xyplot(Sepal.Length + Sepal.Width ~ Petal.Length + Petal.Width | Species,
       data = iris, scales = "free", layout = c(2, 2),
       auto.key = list(x = .6, y = .7, corner = c(0, 0)))
```

## Multivariate Plots

```{r}
splom(~iris[1:4], groups = Species, data = iris)
```


```{r}
super.sym <- trellis.par.get("superpose.symbol")
splom(~iris[1:4], groups = Species, data = iris,
      panel = panel.superpose,
      key = list(title = "Three Varieties of Iris",
                 columns = 3, 
                 points = list(pch = super.sym$pch[1:3],
                 col = super.sym$col[1:3]),
                 text = list(c("Setosa", "Versicolor", "Virginica"))))
```


## parallelplot

```{r}
parallelplot(~iris[1:4] | Species, iris)
```
